DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-06 Draft Ped Metrics Example.Rmd
adds library loop

getWalkingPolygonInCounty <- function(locdf, idcol) {
  # finds the items in locdf that are in the target area
  # then finds the polygon around them
  # then limits that again to the area in the target (because the polygon may go into a city)
  fdf <- st_intersection(locdf, st_buffer(county_no_cities,0)) 
  mb_isochrone(fdf,
               time = 30, "walking", id_column=idcol)
  #fdf <- st_transform(fdf, 9003)
  #st_intersection(fdf, st_buffer(county_no_cities,0)) 
}
library(mapboxapi)
lib_30min <- mb_isochrone(libraries,
               time = 30, "walking", id_column="NAME")
```

Kitsap County has `r nrow(libraries)` Public libraries.

@@

lib_circles <- st_intersection(st_buffer(libraries, 5280), st_buffer(county_no_cities,0)) %>%
  mutate(LENGTH = as.integer(st_length(.)))
lib2 <- getWalkingPolygonInCounty(libraries, "NAME")

kitsap +
  #geom_sf(data = libraries, aes(color = NAME)) +
  geom_sf(data = lib2, aes(fill = id), 
          lwd = 0, alpha = 0.3, show.legend = FALSE) 
  geom_sf(data = lib_circles, aes(fill = NAME), 
          lwd = 0, alpha = 0.3, show.legend = FALSE) +
  geom_sf(data = st_buffer(libraries, 5280), aes(fill = NAME), 
          lwd = 0, alpha = 0.3, show.legend = FALSE) +
  theme_void() +
  labs(title = 'Kitsap County libraries',
       caption = "Data source: Kitsap GIS - data in development",
       color = "Libraries")

@@

>>>>

getWalkingPolygonInCounty <- function(locdf, idcol) {
  # finds the items in locdf that are in the target area
  # then finds the polygon around them
  # then limits that again to the area in the target (because the polygon may go into a city)
  fdf <- st_intersection(locdf, st_buffer(county_no_cities,0)) 
  mb_isochrone(fdf,
               time = 30, "walking", id_column=idcol)
  #fdf <- st_transform(fdf, 9003)
  #st_intersection(fdf, st_buffer(county_no_cities,0)) 
  # doesn't do the clip off of the last part
}
library(mapboxapi)

lib2 <- getWalkingPolygonInCounty(libraries, "NAME")
```

Kitsap County has `r nrow(libraries)` Public libraries; however, only `r nrow(lib2)` are outside of city limits. Here they are shown with a 30 minute walking distance.

@@

#lib_circles <- st_intersection(st_buffer(libraries, 5280), st_buffer(county_no_cities,0))

kitsap +
  geom_sf(data = lib2, aes(fill = id), 
          lwd = 0, alpha = 0.3) +
  geom_sf(data = libraries, aes(color = 1), color = "black", show.legend = FALSE) +
  theme_void() +
  labs(title = 'Kitsap County libraries',
       caption = "Data source: Kitsap GIS - data in development",
       fill = "Libraries")

@@

```{r loop_libraries,include=FALSE,echo=FALSE}
the_libraries <- unique(st_set_geometry(lib2, NULL)$id)
loop_df <- st_as_sf(lib2) %>% mutate(tomatch = id)

score_breakdowns <- score_breakdowns %>%
  bind_rows(tibble(Area = the_libraries, Score = NA))

expanded_child <- lapply(
    the_libraries,
    function(x) {
      knitr::knit_expand(file = "child_single_geo.Rmd",
                                   current_geo = x )
    })

parsed_child <- knitr::knit_child(text = unlist(expanded_child))
```
